Make any stupid plot you want

### 2021-01-22 draft/sections/math.tex
pulled general FB intro back up to set context for unpacking

We first describe the fiber bundle spaces of data(\ref{sec:data}), graphics(\ref{sec:graphic}), and intermediate visual characteristics (\ref{sec:artist}). We then discuss the equivariant maps between data and visual characteristics (\ref{sec:artist_nu}) and visual characteristics and graphics (\ref{sec:artist_q}) that make up the artist.

\subsection{Data Space}
\label{sec:data}
%%% maybe change this to a generic representational data set
We build on Butler's fiber bundle driven abstraction of data formats\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} because fiber bundles can express the properties of the variables(\ref{sec:data_fiber}), the continuity of the records (\ref{sec:data_base}), and distinct instances of records (\ref{sec:data_section}). The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre} unless otherwise specified.

@@

\subsubsection{continuity: Base Space $K$} 
%%fold butlder
\label{sec:data_base}
The fiber provides the schema of the dataset, but the fiber bundle is what glues that schema to a structure. The fiber bundle is the map $\pi$ between the fiber space included in the total space $E$ and the base space $K$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & K
    \end{tikzcd}
\end{equation}

The base space $K$ provides a way to encode how the records are connected to each other; for example the GHCN data can be expressed as discrete observations, many timeseries, maps, a network of stations, etc.

>>>>

We first describe how we model data(\ref{sec:data}), graphics(\ref{sec:graphic}), and intermediate visual characteristics (\ref{sec:artist}) as fiber bundles. We then discuss the equivariant maps between data and visual characteristics (\ref{sec:artist_nu}) and visual characteristics and graphics (\ref{sec:artist_q}) that make up the artist.

\subsection{Data Space}
\label{sec:data}
%%% 
We build on Butler's fiber bundle driven abstraction of data formats\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989},  ....

Fiber bundles are structures $(E,\,B,\,\pi ,\,F)$ where $E$, $F$, and $K$ are topological spaces that encode 
\begin{itemize}
\item the properties of the variables in the fiber $F$ (\ref{sec:data_fiber})
\item the continuity of the records in the base space $K$ (\ref{sec:data_base})
\item collections of records $\tau$ (\ref{sec:data_section}). 
\end{itemize}

where $E$ is the total space of data that $F$ lives in. The bundle is the projection map $\pi$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & K
    \end{tikzcd}
\end{equation}

that binds the variable space $F$ to the base space $K$.

%%probbaly need some more words here maybe, maybe pull that first picture back up now

The fiber bundles mentioned in this work are assumed to be trivial\cite{spanier1989algebraic,LocallyTrivialFibre} unless otherwise specified. In the trivial bundle $E=K\times F$ such that the total space $E$ falls out and discussion can be limited to the $K$ and $F$ spaces.

@@

\subsubsection{continuity: Base Space $K$} 
%%fold butlder
\label{sec:data_base}
The base space $K$ provides a way to encode how the records are connected to each other; for example the GHCN data can be expressed as discrete observations, many timeseries, maps, a network of stations, etc.
